\hmsubsection{Team Organization}{OAH}{UMA}\label{sec:team}

The project group consists of five members with complementary academic backgrounds,
as presented in Table~\ref{tab:group_members}. Four members specialise in Computer
Engineering (Cyber-Physical Systems), while one member specialises in Mechanical
Engineering (Product Development). This interdisciplinary composition was essential
for developing a complete system that integrates mechanical design, embedded systems,
and computer vision software.

The team is organised with clearly defined roles and associated responsibilities.
The Team Leader was responsible for overall coordination and project progress.
The System Lead was responsible for system architecture and integration between
software and hardware components. The Test Lead was responsible for planning and
executing testing and system verification. The Documentation \& Scrum Master was
responsible for maintaining project documentation and facilitating Scrum processes,
including sprint planning, stand-ups, and retrospectives. The Mechanical Engineer
led the physical design of the robot arm, including structural design, material
selection, and physical implementation.

Although roles were clearly defined, the team worked iteratively and collaboratively
throughout the project, with tasks distributed based on both expertise and current
project needs. The tools and communication channels used to support this workflow
are described in Section~\ref{sec:tools-workflow}.
