\hmsubsection{Image Detection Testing}{OAH}{}

An initial detection test was conducted on 29 March 2026 to verify that the vision
pipeline could reliably detect and track red and blue balls in real time. The test
was performed in a home environment with the OAK-D S2 camera mounted
approximately 50\,cm above the workspace surface. Both balls were present in the
frame simultaneously throughout the test, and balls were repeatedly removed and
reintroduced during the session to verify that the tracker correctly handled
disappearance and reappearance events.

The test ran for 72.1 seconds across 1800 frames at an average of 25.0\,FPS,
consistent with the target real-time performance of 20--25\,FPS. The detector
produced 1246 detections of the red ball and 1238 of the blue ball, summarised in
Table~\ref{tab:detection-stats}. Mean confidence scores were 0.829 for red and
0.824 for blue, with standard deviations of 0.062 and 0.075 respectively. All
accepted detections exceeded the minimum confidence threshold of 0.50, and no
detections fell below 0.577.

Detection was performed almost exclusively by the HSV segmentation method (2491
out of 2492 total detections). The Hough Circle Transform contributed zero
independent detections, and ensemble merging produced one combined detection.
This distribution is consistent with the test conditions: the HSV pipeline is the
primary method under stable, controlled lighting, while the Hough transform
provides redundancy under conditions where colour segmentation is less reliable.

The tracker successfully followed both balls during continuous movement and
correctly re-acquired them after removal and reintroduction. Prior to this test,
false positives had been observed under certain lighting conditions. These were
addressed through refinement of the HSV thresholds and geometric gate filters
before the test session reported here, and no false positives were observed during
the 72.1-second recording.

This test was conducted during early development as an isolated verification of
the vision pipeline, prior to integration with the robotic arm. End-to-end
system testing, including sorting accuracy and system reliability, is described
in the sections below.

\begin{table}[H]
    \centering
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{|l|r|r|r|}
        \hline
        \textbf{Metric} & \textbf{Red ball} & \textbf{Blue ball} & \textbf{Total} \\
        \hline
        Number of detections    & 1246  & 1238  & 2484 \\
        \hline
        Mean confidence         & 0.829 & 0.824 & --   \\
        \hline
        Std.\ confidence        & 0.062 & 0.075 & --   \\
        \hline
        Min confidence          & 0.637 & 0.577 & --   \\
        \hline
        Max confidence          & 0.915 & 0.884 & --   \\
        \hline
        Number of frames        & --    & --    & 1800 \\
        \hline
        Test duration (s)       & --    & --    & 72.1 \\
        \hline
        Mean FPS                & --    & --    & 25.0 \\
        \hline
        HSV detections          & --    & --    & 2491 \\
        \hline
        Hough detections        & --    & --    & 0    \\
        \hline
        Ensemble detections     & --    & --    & 1    \\
        \hline
    \end{tabular}
    \caption[Detection statistics, 29 March 2026.]{Detection statistics
    from the initial vision pipeline test conducted on 29 March 2026.}
    \label{tab:detection-stats}
\end{table}