\hmsubsection{MVP Verification}{UMA}{}\label{sec:mvp-verification}

This section presents the end-to-end verification of the minimum
viable product defined in Section~\ref{sec:mvp}. The purpose is to
demonstrate that the system can autonomously detect, pick, and
sort coloured balls into the correct bins.

\hmsubsubsection{Test Setup}{UMA}{}

The final MVP validation was conducted under the following
conditions:

\begin{itemize}
    \item \textbf{Balls:} 20~sorting cycles were completed with
    10~red and 10~blue spherical balls.
    \item \textbf{Lighting:} Standard laboratory lighting under
    the tested laboratory conditions. No additional lighting
    condition or lux value is claimed for this validation session.
    \item \textbf{Configuration:} Touch calibration and bin
    calibration completed. System running in production mode
    (\texttt{python src/main.py --real-serial --real-camera}).
    The console log confirmed a real serial connection to the
    OpenRB-150, a real OAK-D camera, a ready inverse kinematics
    solver, an OpenRB handshake, and verified adaptive grip
    feedback before the repeated scan-pick-place cycles.
    \item \textbf{Camera warm-up:} 30~seconds of auto-exposure
    stabilisation before the first cycle.
    \item \textbf{Run continuity:} The system was not restarted
    between cycles. One additional grip-verification rejection
    occurred during cycle~7; grip verification correctly rejected
    an unstable grasp, and the retry logic recovered the cycle on
    the next scan. The event did not become an unrecovered sorting
    failure.
\end{itemize}

\hmsubsubsection{Procedure}{UMA}{}

The system was run for 20 consecutive sorting cycles. Each cycle
consisted of: scan (camera detection), approach (IK solve and arm
movement), grab (adaptive grip with verification), sort movement,
and drop (claw open over the correct bin). A ball was counted as
sorted correctly only if it ultimately reached the correct bin.
A failure was counted as unrecovered only if the system did not
recover during the run and the ball did not reach the correct
bin. Consequently, the recovered grip-verification event in
cycle~7 is reported separately from unrecovered sorting failures.

\hmsubsubsection{Results}{UMA}{}

\begin{table}[H]
    \centering
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{|l|r|r|r|}
        \hline
        \textbf{Metric} & \textbf{Count} &
        \textbf{Total} & \textbf{Result} \\
        \hline
        Net balls sorted correctly & 20 & 20 & 100\% \\
        \hline
        Blue balls picked and placed & 10 & 10 & 100\% \\
        \hline
        Red balls picked and placed & 10 & 10 & 100\% \\
        \hline
        Unrecovered failures & 0 & 20 & 0\% \\
        \hline
        Additional grip-verification rejections & 1 & -- & Recovered \\
        \hline
    \end{tabular}
    \caption{Final MVP validation results over 20 completed
    sorting cycles. The additional grip-verification rejection
    occurred in cycle~7 on a red ball, was recovered by retry
    logic on the next scan, and did not prevent correct final
    placement.}
    \label{tab:mvp-final-results}
\end{table}

\hmsubsubsection{Timing Summary}{UMA}{}

\begin{table}[H]
    \centering
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{|l|r|r|r|r|}
        \hline
        \textbf{Phase} & \textbf{Average (s)} &
        \textbf{Minimum (s)} & \textbf{Maximum (s)} &
        \textbf{$n$} \\
        \hline
        Scan & 3.11 & 2.87 & 5.83 & 20 \\
        \hline
        Approach & 1.67 & 1.55 & 1.77 & 20 \\
        \hline
        Grab & 1.54 & 1.41 & 2.89 & 20 \\
        \hline
        Sort & 2.78 & 2.68 & 2.94 & 20 \\
        \hline
        Drop & 3.64 & 3.31 & 4.15 & 20 \\
        \hline
        Total cycle time & 12.75 & 12.13 & 16.68 & 20 \\
        \hline
    \end{tabular}
    \caption{Timing summary from the final 20-cycle MVP
    validation session. The maximum scan and grab values include
    the retry-recovered cycle~7 event.}
    \label{tab:mvp-final-timing}
\end{table}

\hmsubsubsection{Assessment}{UMA}{}

The minimum viable product required the system to complete at
least 10~consecutive autonomous sorting cycles with a detection
rate above 90\%, a pick success rate above 80\%, and 100\%
correct bin placement given a correct colour classification.

Based on the results in Table~\ref{tab:mvp-final-results}, the
system achieved the MVP under the tested laboratory conditions.
The final validation session sorted 20/20 balls correctly
(100\% observed net sorting success) with 0 unrecovered failures.
Blue and red performance were both 10/10 for picked and placed
balls. This net sorting result is distinct from grip-attempt
behaviour: one additional grip-verification rejection occurred in
cycle~7 before successful retry. Grip verification correctly
rejected an unstable grasp, and retry logic recovered the cycle
on the next scan; because the ball was ultimately placed in the
correct bin, this event did not reduce the final net sorting
result. The timing results in Table~\ref{tab:mvp-final-timing}
show an average total cycle time of 12.75~s over the 20
completed cycles, corresponding to approximately 4.7~balls/min
for this validation session.
