\hmsubsection {Sorting Accuracy}{FKT}{

Sorting accuracy was evaluated using the final MVP validation
session as the authoritative integrated result. In this session,
the system operated with the real OAK-D camera, a real serial
connection to the OpenRB-150, completed controller handshake,
ready inverse kinematics solver, and adaptive grip verification.
The test therefore measured the combined perception, motion,
gripping, and bin-placement behaviour rather than an isolated
software-only classification result.

The final validation session consisted of 20 completed sorting
cycles and 20 balls. The net result was \textbf{20/20 balls sorted
correctly (100\% observed net sorting success)} with \textbf{0
unrecovered failures}. Both colour classes achieved the same
final result: 10/10 blue balls were picked and placed correctly,
and 10/10 red balls were picked and placed correctly. One
additional grip-verification rejection occurred in cycle~7 on a
red ball before successful retry. Grip verification correctly
rejected an unstable grasp, and retry logic recovered the cycle
on the next scan. It is therefore reported separately from the
net sorting result, not as an unrecovered sorting failure.

\begin{table}[H]
\centering
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{|l|r|r|r|}
\hline
\textbf{Sorting category} & \textbf{Correct} & \textbf{Total} &
\textbf{Observed result} \\
\hline
Blue balls picked and placed & 10 & 10 & 100\% \\
\hline
Red balls picked and placed & 10 & 10 & 100\% \\
\hline
Overall net sorting result & 20 & 20 & 100\% \\
\hline
Unrecovered sorting failures & 0 & 20 & 0\% \\
\hline
\end{tabular}
\caption{Sorting accuracy in the final 20-ball validation
session.}
\label{tab:sorting-accuracy-final}
\end{table}

These results demonstrate that the MVP sorting objective was
achieved under the tested laboratory conditions. The result
should not be interpreted as a claim of perfect general
reliability across all possible environments or object
presentations; it documents the measured performance in the
final integrated validation session.
}
