\begin{titlepage}
    \newgeometry{left=0cm,right=0cm,top=0cm,bottom=0cm}
    \parindent0pt
    
    % Light theme palette
    \definecolor{lightbg}{RGB}{252, 252, 250}
    \definecolor{panelbg}{RGB}{245, 245, 243}
    \definecolor{accent}{RGB}{20, 160, 90}
    \definecolor{darktext}{RGB}{15, 18, 22}
    \definecolor{softgray}{RGB}{110, 115, 120}
    \definecolor{midgray}{RGB}{160, 165, 170}
    
    \begin{tikzpicture}[remember picture, overlay]
        % ===== FULL LIGHT BACKGROUND =====
        \fill[lightbg] (current page.north west) rectangle (current page.south east);
        
        % ============================================================
        % TOP — STATUS PILL + PAGE INDICATOR
        % ============================================================
        \node[anchor=north west, draw=accent, line width=1pt, rounded corners=2pt,
              inner xsep=14pt, inner ysep=8pt,
              font=\sffamily\bfseries\small, text=accent] 
            at ([xshift=2.5cm, yshift=-2cm]current page.north west) 
            {\textcolor{accent}{$\bullet$}~~ABSTRACT};
        
        \node[anchor=north east, text=softgray, font=\sffamily\small] 
            at ([xshift=-2.5cm, yshift=-2cm]current page.north east) 
            {03 / SUMMARY};
        
        % ============================================================
        % FOOTER
        % ============================================================
        \draw[midgray, line width=0.5pt] 
            ([xshift=2.5cm, yshift=1.8cm]current page.south west) -- 
            ([xshift=-2.5cm, yshift=1.8cm]current page.south east);
        
        \node[anchor=south west, text=softgray, font=\sffamily\footnotesize] 
            at ([xshift=2.5cm, yshift=1cm]current page.south west) 
            {UNIVERSITY OF SOUTH-EASTERN NORWAY \textcolor{accent}{$\bullet$} CAMPUS KONGSBERG};
        
        \node[anchor=south east, text=softgray, font=\sffamily\footnotesize] 
            at ([xshift=-2.5cm, yshift=1cm]current page.south east) 
            {BACHELOR THESIS / 2026};
    \end{tikzpicture}
    
    \addcontentsline{toc}{section}{Abstract}
    
    \vspace*{3cm}
    
    \hspace{2.5cm}\begin{minipage}{15cm}
        {\sffamily\bfseries\fontsize{11}{13}\selectfont\textcolor{darktext}{A~~U~~T~~O~~N~~O~~M~~I~~A}}
        
        \vspace{0.3cm}
        
        {\fontsize{38}{42}\selectfont\itshape\textcolor{darktext}{The}}\\[0cm]
        {\fontsize{38}{42}\selectfont\bfseries\textcolor{darktext}{Abstract.}}
        
        \vspace{0.3cm}
        
        {\color{accent}\rule{3cm}{2pt}}
        
        \vspace{1.2cm}
        
        % ============================================================
        % BODY TEXT — normal size matching the rest of the thesis
        % ============================================================
        \color{darktext}
        \normalsize
        
        This project presents the development of an autonomous robotic system capable of 
        detecting, classifying, and sorting red and blue spherical objects in real time. 
        A Luxonis OAK-D Series~2 camera mounted above the workspace captures image data, 
        which is processed on a Raspberry Pi~5 through a deterministic computer vision 
        pipeline. The system then directs a six-axis robotic arm to physically sort the 
        detected balls into designated containers.
        
        \vspace{0.4cm}
        
        The vision pipeline combines multi-range HSV colour segmentation, Hough Circle 
        Transform, and geometric contour validation into an ensemble detection system. 
        Detections from multiple methods are merged using a Union-Find structure and 
        filtered through Non-Maximum Suppression. Adaptive lighting compensation via 
        CLAHE ensures robust performance across ambient conditions ranging from 
        300 to 700\,lux. A Support Vector Machine classifier was initially evaluated 
        as a secondary colour-verification step but was disabled in the final 
        implementation after it was found to misclassify dark navy-blue balls as red.
        
        \vspace{0.4cm}
        
        A classical, deterministic approach was chosen over learning-based methods such 
        as convolutional neural networks. MobileNetV2 transfer learning was evaluated 
        during early development but produced inference times of 200--500\,ms per frame 
        on the target hardware, making it unsuitable for real-time operation. The 
        proposed pipeline achieves 20--25\,FPS with a detection rate of 98--100\,\% 
        and a false positive rate below 2\,\% under laboratory conditions, without 
        requiring large labelled training datasets.
        
        \vspace{0.4cm}
        
        The system is fully explainable: every detection rejection has a specific 
        geometric or chromatic cause traceable through the pipeline, making it 
        well-suited for controlled sorting environments where predictable and 
        diagnosable behaviour is required.
        
        \vspace{1.2cm}
        
        % Keyword tags
        {\textcolor{softgray}{\footnotesize\textsc{Keywords:}}~~
        \textcolor{darktext}{\sffamily\footnotesize Computer Vision \textcolor{accent}{$\cdot$} 
        Robotic Sorting \textcolor{accent}{$\cdot$} HSV Segmentation \textcolor{accent}{$\cdot$} 
        Real-Time Systems \textcolor{accent}{$\cdot$} Raspberry Pi}}
    \end{minipage}
    
    \restoregeometry
\end{titlepage}