\hmsubsection{MVP Verification}{UMA}{}

This section presents the end-to-end verification of the minimum
viable product defined in Section~3.3. The purpose is to
demonstrate that the system can autonomously detect, pick, and
sort coloured balls into the correct bins without human
intervention.

\hmsubsubsection{Test Setup}{UMA}{}

The verification was conducted under the following conditions:

\begin{itemize}
    \item \textbf{Balls:} 5~red and 5~blue spherical balls,
    50~mm diameter, placed at varied positions spanning the
    reachable workspace (12--36~cm from the shoulder, $\pm$12~cm
    lateral).
    \item \textbf{Lighting:} Standard laboratory lighting at
    approximately \textbf{[TBD]}~lux, as reported by the
    detector's automatic lighting analysis.
    \item \textbf{Configuration:} Touch calibration and bin
    calibration completed. System running in production mode
    (\texttt{python src/main.py --real-serial --real-camera}).
    \item \textbf{Camera warm-up:} 30~seconds of auto-exposure
    stabilisation before the first cycle.
    \item \textbf{No intervention:} The operator did not touch
    the arm or the balls during any cycle. The system was not
    restarted between cycles.
\end{itemize}

\hmsubsubsection{Procedure}{UMA}{}

The system was run for \textbf{[TBD]} consecutive autonomous
sorting cycles. Each cycle consisted of: scan (camera detection),
approach (IK solve and arm movement), grab (adaptive grip with
verification), transport (route to bin), and drop (claw open over
the correct bin). A cycle was counted as successful only if the
ball was detected, picked, and placed into the correct bin. A
cycle was counted as failed if any stage produced an incorrect
result: missed detection, failed pick, wrong bin, or ball dropped
during transport.

\hmsubsubsection{Results}{UMA}{}

\begin{table}[H]
    \centering
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{|c|c|c|c|c|l|}
        \hline
        \textbf{Cycle} & \textbf{Colour} &
        \textbf{Detected} & \textbf{Picked} &
        \textbf{Correct bin} & \textbf{Notes} \\
        \hline
        1  & Red  & \textbf{[TBD]} & \textbf{[TBD]} &
        \textbf{[TBD]} & \\
        \hline
        2  & Blue & \textbf{[TBD]} & \textbf{[TBD]} &
        \textbf{[TBD]} & \\
        \hline
        3  & Red  & \textbf{[TBD]} & \textbf{[TBD]} &
        \textbf{[TBD]} & \\
        \hline
        4  & Blue & \textbf{[TBD]} & \textbf{[TBD]} &
        \textbf{[TBD]} & \\
        \hline
        5  & Red  & \textbf{[TBD]} & \textbf{[TBD]} &
        \textbf{[TBD]} & \\
        \hline
        6  & Blue & \textbf{[TBD]} & \textbf{[TBD]} &
        \textbf{[TBD]} & \\
        \hline
        7  & Red  & \textbf{[TBD]} & \textbf{[TBD]} &
        \textbf{[TBD]} & \\
        \hline
        8  & Blue & \textbf{[TBD]} & \textbf{[TBD]} &
        \textbf{[TBD]} & \\
        \hline
        9  & Red  & \textbf{[TBD]} & \textbf{[TBD]} &
        \textbf{[TBD]} & \\
        \hline
        10 & Blue & \textbf{[TBD]} & \textbf{[TBD]} &
        \textbf{[TBD]} & \\
        \hline
    \end{tabular}
    \caption{Per-cycle results of the MVP verification test.
    Each row records whether the ball was detected, successfully
    picked, and placed in the correct bin.}
\end{table}

\hmsubsubsection{Summary}{UMA}{}

\begin{table}[H]
    \centering
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{|l|r|}
        \hline
        \textbf{Metric} & \textbf{Result} \\
        \hline
        Total cycles attempted &
        \textbf{[TBD]} \\
        \hline
        Detection rate &
        \textbf{[TBD]} / \textbf{[TBD]}
        (\textbf{[TBD]}\%) \\
        \hline
        Pick success rate &
        \textbf{[TBD]} / \textbf{[TBD]}
        (\textbf{[TBD]}\%) \\
        \hline
        Correct bin placement rate &
        \textbf{[TBD]} / \textbf{[TBD]}
        (\textbf{[TBD]}\%) \\
        \hline
        Full cycle success rate &
        \textbf{[TBD]} / \textbf{[TBD]}
        (\textbf{[TBD]}\%) \\
        \hline
        Longest consecutive successes &
        \textbf{[TBD]} \\
        \hline
    \end{tabular}
    \caption{Aggregate performance metrics from the MVP
    verification test.}
\end{table}

\hmsubsubsection{Assessment}{UMA}{}

% ── FILL THIS IN AFTER TESTING ──
% Be honest. State which requirements are met and which are not.
% Example text (replace with actual results):

The minimum viable product required the system to complete at
least 10~consecutive autonomous sorting cycles with a detection
rate above 90\%, a pick success rate above 80\%, and 100\%
correct bin placement given a correct colour classification.

Based on the results in Table~\textbf{[TBD]}, the system
achieved \textbf{[TBD]}~consecutive successful cycles with a
pick success rate of \textbf{[TBD]}\% and a placement accuracy
of \textbf{[TBD]}\%. \textbf{[State which requirements are met
and which are not. If the MVP was not fully achieved, explain
what failed and why. Be specific: e.g.\ ``the ball was lost
during transport in 2 of 10 cycles due to insufficient grip
force at extended reach.'']}
